The Practical Application of MST

### 2021-02-17 article.Rmd
Added Cronbach's alpha calculations

print(cutoff)
```

@@

print(dfSampleResponse)
```

@@

```{r show simulated test, echo=TRUE}
plot(dfMSTResponse)
```

@@

The `ltm` library can be used to fit a number of dichotomous and polytomous IRT models. Its the fastest library that I've found for fitting a Rasch model. First we get some summary statistics from the data, including

@@

# return descriptive stats such as Cronbach's alpha
descript <- ltm::descript(dfTrial, chi.squared = FALSE)

# graph the frequencies of the total scores
dfFreqs <- enframe(descript$items[1:length(descript$items)],
                   name = "testscore", value = "frequency")

ggplot(data = dfFreqs) +
  geom_bar(mapping = aes(x = testscore, y = frequency), stat = "identity") +
  xlim(0, 40)
```

>>>>

(cutoff)
```

@@

(dfSampleResponse)
```

@@

```{r show simulated test, echo=FALSE}
plot(dfMSTResponse)
```

@@

The `ltm` library can be used to fit a number of dichotomous and polytomous IRT models. Its the fastest library that I've found for fitting a Rasch model. Before doing that we get some summary statistics from the data, including the Cronbach's alpha measure of covariance. Cronbach's alpha is a function of the number of items in a test, the average covariance between pairs of items, and the variance of the total score. In our test we've split our items into different modules according to the skill that is being measured, so it makes sense to calculate alphas for each module, although we could also do so by stage. We need to make sure that we remove any rows containing NA values before calculating Cronbach's alpha.

@@

# its sometimes useful to see the the average covariances between pairs of items and compare this with the variance of the total score.
# this can be done on a per-module basis using the Cronbach's alpha measure of covariance
# to usefully use this we'll need to work out this measure on a per-module basis
dfModuleAItems <- dfTrial %>% dplyr::select(1:12) %>% na.omit()
dfModuleBItems <- dfTrial %>% dplyr::select(13:20) %>% na.omit()
dfModuleCItems <- dfTrial %>% dplyr::select(21:28) %>% na.omit()
dfModuleDItems <- dfTrial %>% dplyr::select(29:38) %>% na.omit()
dfModuleEItems <- dfTrial %>% dplyr::select(39:48) %>% na.omit()
dfModuleFItems <- dfTrial %>% dplyr::select(49:58) %>% na.omit()
dfModuleGItems <- dfTrial %>% dplyr::select(59:68) %>% na.omit()

alphasModuleA <- ltm::cronbach.alpha(dfModuleAItems)
alphasModuleB <- ltm::cronbach.alpha(dfModuleBItems)
alphasModuleC <- ltm::cronbach.alpha(dfModuleCItems)
alphasModuleD <- ltm::cronbach.alpha(dfModuleDItems)
alphasModuleE <- ltm::cronbach.alpha(dfModuleEItems)
alphasModuleF <- ltm::cronbach.alpha(dfModuleFItems)
alphasModuleG <- ltm::cronbach.alpha(dfModuleGItems)

moduleNames <- c('A', 'B', 'C', 'D', 'E', 'F', 'G')
alphas <- c(alphasModuleA$alpha, alphasModuleB$alpha, alphasModuleC$alpha,
            alphasModuleD$alpha, alphasModuleE$alpha, alphasModuleF$alpha,
            alphasModuleG$alpha)
num_items <- c(alphasModuleA$p, alphasModuleB$p, alphasModuleC$p,
            alphasModuleD$p, alphasModuleE$p, alphasModuleF$p,
            alphasModuleG$p)
num_responses <- c(alphasModuleA$n, alphasModuleB$n, alphasModuleC$n,
            alphasModuleD$n, alphasModuleE$n, alphasModuleF$n,
            alphasModuleG$n)
```
